---
title: "p8105_hw1_yf2605"
author: "Yi_Fang"
date: "`r Sys.Date()`"
output: html_document
---

# Libraries

```{r}
library(tidyverse)
```

# Problem 1

## load the penguins data set:

```{r}
data("penguins", package = "palmerpenguins")
```

## Description:
Summary of the data set:
```{r} 
summary(penguins)
```

*  There are `r ncol(penguins)` variables and `r nrow(penguins)` records in the penguins data set.
*  The variables include: `r colnames(penguins)` 
*  According to the dataset, the mean flipper length is `r round(mean(penguins$flipper_length_mm, na.rm = TRUE), digits = 2)` mm. 

## Scatter plot for flipper length vs bill length:
```{r}
ggplot(penguins, 
  aes(x = bill_length_mm, 
      y = flipper_length_mm, 
      color = species)) + geom_point()

ggsave("scatter_plot.png", height = 4, width = 6)
```

# Problem 2

## create the data frame

```{r}
df = tibble(random_num = rnorm(10),
            logical_vec = (random_num > 0),
            char_vec = c('a', 'b', 'c', 'd', 'e', 'f', 'g', 'h', 'i', 'j'),
            factor_vec = factor(c("l", "m", "s", "s", "s", "l", "l", "m", "m", "l")))
df
```

## take mean

```{r}
mean(pull(df, random_num))
mean(pull(df, logical_vec))
mean(pull(df, char_vec))
mean(pull(df, factor_vec))
```
`mean()` works for numeric and logical variables but doesn’t work for character and factor variables. 

## `as.numeric` fuction
```{r eval=FALSE}
as.numeric(pull(df, logical_vec))
as.numeric(pull(df, char_vec))
as.numeric(pull(df, factor_vec))
```
*  The logical variable is converted to 0 and 1
*  The character variable is converted to NA by coercion
*  factor variable is converted to 1,2 and 3\
This explains the mean of the logical variable.
